---
title: "Analysis of sustainability disclosure of food retailers in Europe"
author: "Johannes W.H. van der Waal"
date: "7-3-2022"
output:   html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(quanteda)
library(tidyverse)
```

# Objective

- objectively chart the sustainability themes of food retailers
- identify relevant topics that we must not miss
- match our sustainability focus areas with those of retailers

# Method
```{r stats1, echo=FALSE, message = FALSE}

#load bulk data
load("mat_mr.Rdata")

library(readxl)
company_names <- read_excel("company_names.xlsx") 

#construct corpus
corp_mr <- quanteda::corpus(mat_mr)

#make corpus subset based on language
corp_en <- corpus_subset(corp_mr, language == "EN")
docvars <- docvars(corp_en)

# number of English reports
nrow(docvars)
```
- Text analysis of `r nrow(docvars)` sustainability reports.
- Non-English reports were converted to English language with Deepl.com
- Supervised and non-supervised thematic analysis 

```{r stats2, eval = TRUE, echo = FALSE}
# retrieve text stats by company
load("raw_stats.Rda")
clean_stats <- raw_stats %>% 
  mutate(company = substr(document, 12,19)) %>%
  left_join(.,company_names) 
```
## Description of the reports
```{r plot, eval=TRUE, echo = FALSE, message = FALSE}
library(ggthemes)
library(ggrepel)
#determine order og high to low sentence scores for ggplot
order <- clean_stats %>% 
  group_by(retailer) %>%
  summarize(zinnen = sum(sents), country= as.factor(country), retailer = as.factor(retailer)) %>% 
  unique() %>%
  group_by(country) %>%
  summarize(z = sum(zinnen)) %>%
  arrange(desc(z)) %>%
  pull(country)

p <- clean_stats %>% 
  group_by(retailer) %>%
  summarize(zinnen = sum(sents), country= as.factor(country), retailer = as.factor(retailer)) %>%
  unique() %>%
  ggplot(aes(reorder(country, -zinnen), zinnen, label = retailer, fill = retailer)) +
  geom_bar(stat = "identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  ggtitle("Number of sentences in food retail sustainability reports per country") +
  xlab("country") + ylab("Number of sentences") +
  theme_economist() 
p + theme(legend.position="none") +
  scale_x_discrete(limits=order) #this puts the columns in the order of the highest to lowest
  coord_flip() 

```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
